Exploring the Evolution of Energy in Radiohead's Music

### 2024-10-10 paper/paper.qmd
upload the file

@@

# Plot the distribution of energy across albums
ggplot(radiohead, aes(x = album_name, y = energy, fill = album_name)) +
  geom_boxplot() +
  labs(x = "Album",
       y = "Energy") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

@@

```
@fig-valence illustrates the relationship between energy and valence (positivity) in Radiohead's songs. Each blue dot represents a song, with the X-axis showing valence (the positivity of the emotion) and the Y-axis showing energy levels. The red regression line indicates a positive correlation between the two variables, suggesting that as valence increases, the energy of the song tends to rise as well.

```{r}
#| echo: false
#| warning: false
#| label: fig-loudness
#| fig-cap: "Relationship between Loudness and Energy in Radiohead's Songs"
#| 
# Plot the relationship between energy and loudness
ggplot(radiohead, aes(x = loudness, y = energy)) +
  geom_point(alpha = 0.7, color = "darkgreen") +
  geom_smooth(method = "lm", se = FALSE, color = "red") + 
  labs(x = "Loudness (dB)",
       y = "Energy") +
  theme_minimal()
```
@fig-loudness shows the relationship between energy and loudness in Radiohead's songs. Each green dot represents a song, with the X-axis indicating the loudness (measured in decibels) and the Y-axis indicating the energy level. The red regression line reveals a strong positive correlation between these two variables, where louder songs generally tend to have higher energy.

@@

>>>>

The remainder of this paper is structured as follows. @sec-data discusses overview dataset including variables such as energy, album release year, loudness, valence, and album name, and it also includes tools used for data analysis and visualization. The results of the main findings of the analysis through visualizations is also included in @sec-data, including Energy Over Time, Energy by Album,Relationship Between Valence and Energy, and Relationship Between Loudness and Energy. @sec-discussion interprets the results further with more consideration. @sec-conclusion summarizes the key insights from the analysis, emphasizing the evolution of energy in Radiohead’s music and the role of valence and loudness in shaping song intensity. @sec-appendix provides details on gathering data from Spotify using the spotifyr R package, including steps for retrieving and securely storing data.

@@

# Plot the distribution of energy across albums
ggplot(radiohead, aes(x = album_name, y = energy, fill = album_name)) +
  geom_boxplot() +
  geom_point() +
  labs(x = "Album",
       y = "Energy") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

@@

```
@fig-valence illustrates the relationship between valence (positivity) and energy levels in Radiohead’s songs. Each blue dot represents a song, with valence reflecting the positivity of the emotion and energy capturing the intensity of the song. The red regression line indicates a positive correlation, suggesting that as the valence increases, the energy of the song tends to rise as well. This implies that Radiohead’s songs with more positive emotions generally have higher energy.

```{r}
#| echo: false
#| warning: false
#| label: fig-loudness
#| fig-cap: "Relationship between Loudness and Energy in Radiohead's Songs"
#| 
# Plot the relationship between energy and loudness
ggplot(radiohead, aes(x = loudness, y = energy)) +
  geom_point(alpha = 0.7, color = "darkgreen") +
  geom_smooth(method = "lm", se = FALSE, color = "red") + 
  labs(x = "Loudness (dB)",
       y = "Energy") +
  theme_minimal()
```
@fig-loudness shows the relationship between energy and loudness in Radiohead's songs. The red regression line running diagonally across the plot highlights a clear positive trend: as loudness increases, energy levels tend to rise as well. This suggests that Radiohead's louder songs are generally more energetic, which aligns with the expectation that dynamic and loud compositions often carry higher energy. The spread of points around the regression line shows some variability, but the overall correlation remains strong, as evidenced by the concentration of points close to the red line.

@@

\appendix
